Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics

### 2015-04-29 paper.tex
removidas rebarbas

\begin{table}[h]
	\caption{Example of activity percentages along the hours of the day. Higher activity was observed between noon and 6pm, followed by the time period between 6pm and midnight. Around 2/3 of the whole activity takes place from noon to midnight. Nevertheless, the activity peak occurs around midday, with a slight skew toward one hour before noon.}
	\footnotesize
	\input{tables/tabHoursCPP_}
\label{tab:hin}
\end{table}

\FloatBarrier
\begin{table}
	\caption{Example of activity percentages along the days of the week. Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.}
\begin{center}
    \begin{tabular}{ | l |  c | c | c | c | c |   c | c |}
        \hline
        & Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
	\input{tables/tabWeekdays}
    \end{tabular}
\end{center}
\label{tab:win}
\end{table}

@@

@@

\begin{table}[!h]
    \caption{Distribution of activity among participants. The first column presents the percentage of messages sent by the most active participant. The column for the first quartile ($1Q$) shows the minimum percentage of participants responsible for at least 25\% of total messages. Similarly, the column for the first three quartiles $1-3Q$ gives the minimum percentage of participants responsible for 75\% of total messages. The last decile $-10D$ column brings the maximum percentage of participants responsible for 10\% of messages.}
\begin{center}
    \begin{tabular}{ | l ||  c | c | c | c | }
        \hline
        list & hub & $ 1Q $ & $ 1-3Q $ & $-10D$ \\ \hline
	\input{tables/userTab}
    \end{tabular}
\end{center}
\label{autores}
\end{table}

@@

Further work should inspect other topological measures in each sector.
The subtraction $\widetilde{P}(k)-P(k)$ (see Section~\ref{subsec:typ}) results in two positive clusters for periphery and hubs, and a negative cluster for intermediary vertices. This might support classification of the three sectors by clustering, a more traditional approach to classification.
Observance of attributes with greater contribution to principal components of LDA should reveal best chances to present these three sections as clusters in the network measurements space. 
Another possibility, especially for a brute-force characterization of such sectors, is to remove vertices with degree close to $k_\Leftarrow$ or $k_\Rightarrow$ depicted in figure~\ref{fig:setores}.

@@

\section{Tables}\label{sectables}
\subsection{PCA tables}\label{sec:pcat}

>>>>

\begin{table}
	\caption{Example of activity percentages along the hours of the day. Higher activity was observed between noon and 6pm, followed by the time period between 6pm and midnight. Around 2/3 of the whole activity takes place from noon to midnight. Nevertheless, the activity peak occurs around midday, with a slight skew toward one hour before noon.}
	\footnotesize
	\input{tables/tabHoursCPP_}
\label{tab:hin}
\end{table}

\begin{table}
	\caption{Example of activity percentages along the days of the week. Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.}
\begin{center}
    \begin{tabular}{ | l |  c | c | c | c | c |   c | c |}
        \hline
        & Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
	\input{tables/tabWeekdays}
    \end{tabular}
\end{center}
\label{tab:win}
\end{table}

@@

\FloatBarrier

@@

\begin{table}[h]
    \caption{Distribution of activity among participants. The first column presents the percentage of messages sent by the most active participant. The column for the first quartile ($1Q$) shows the minimum percentage of participants responsible for at least 25\% of total messages. Similarly, the column for the first three quartiles $1-3Q$ gives the minimum percentage of participants responsible for 75\% of total messages. The last decile $-10D$ column brings the maximum percentage of participants responsible for 10\% of messages.}
\begin{center}
    \begin{tabular}{ | l ||  c | c | c | c | }
        \hline
        list & hub & $ 1Q $ & $ 1-3Q $ & $-10D$ \\ \hline
	\input{tables/userTab}
    \end{tabular}
\end{center}
\label{autores}
\end{table}

@@

Further work should inspect other topological measures in each sector.
The subtraction $\widetilde{P}(k)-P(k)$ results in two positive clusters for periphery and hubs, and a negative cluster for intermediary vertices. This might support classification of the three sectors by clustering, a more traditional approach to classification.
Observance of attributes with greater contribution to principal components of LDA should reveal best chances to present these three sections as clusters in the network measurements space. 
Another possibility, especially for a brute-force characterization of such sectors, is to remove vertices with degree close to $k_\Leftarrow$ or $k_\Rightarrow$ depicted in figure~\ref{fig:setores}.

@@

%\section{Tables}\label{sectables}
%\subsection{PCA tables}\label{sec:pcat}
